---
title       : Presidential Candidates 2016  
subtitle    : Donations and Spenditure
author      : Frederik Nyssens  
job         : Developing Data Products
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap]            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft}
knit        : slidify::knit2slides
---


## How much did presedential candidates recieve in donations and spend for the presedential elections in 2016? 

### Methodology 
* Data cleaning 
* UI -  Reactive widget in the candidates selection 
* UI -  Submit button  
* Server - Data sorting is the same for every visaulisation 
* Server -  Map : gvisGeoChart from GoogleVis
* Server - Plot : ggplot
* Server - Table : renderDataTable  from Shiny
* Presentation : 2 ggplots to  fill 5 pages and have some r code executed 


--- .class #id 
## Presidential Candidates Donations 

```{r echo=FALSE, warning=FALSE, , warning=FALSE, fig.width = 14}
candidatesData <- read.csv(file = "../../shinyapps/code/data/combinedData.csv", header = T, as.is = T)
library(ggplot2)
library(dplyr)
plot <- candidatesData %>% filter(Amount > 0) %>% group_by(Date) %>% summarise(Amount = sum(Amount)) %>% ggplot( aes(x = Date, y = Amount, group = 1))
plot + geom_smooth(method="loess", se = FALSE) + geom_point()

```

--- .class #id 

## Presidential Candidates Expenses 

```{r echo=FALSE, fig.width = 14 }
plot <- candidatesData %>% filter(Amount < 0) %>% group_by(Date) %>% summarise(Amount = sum(Amount)) %>% ggplot( aes(x = Date, y = Amount, group = 1))
plot + geom_smooth(method="loess", se = FALSE) + geom_point()
```

--- .class #id 

## Possible additions  

* Add some CSS to make it look better 
* Add polictical parties (Dem, GOP, independent) to the candididates 
* Add public events calendar to visualise the effect 
* Do some actual data science 

## Links 

* [Github Code](https://github.com/StartFinishing/DataProducts)
* [Shiny App](https://startfinishing.shinyapps.io/PresidentialCandidates)
* [Data - Obtained from FEC, 2016 Presidential Elections](http://www.fec.gov/portal/presidential.shtml)


